Conversas Hiperligadas: Novo Paradigma de Comunicação e Colaboração, potenciado pela Tecnologia WebRTC

### 2016-04-07 tese2/evaluation.tex
[FIX] memory leak ready for new performance tests
[ADD] client side tests

      We are presenting in this sections the results of our performance tests after implementing our solution.

@@

@@

@@

>>>>

      We are presenting in this section the results of our performance tests after implementing our solution.
\subsubsection{Network usage}

@@

On the other hand figure \ref{fig:test_client_net} shows the respective network usage on the client side during our test case. We observe that int he first seconds the client adjusts the video quality that sends to \ac{KMS}, whenever a new client enters in the conference we observer that \ac{KMS} decreases the video quality in order to instantaneously integrate a new user into the conference room, after a while \ac{KMS} realizes that its network can handle the increase of clients and sends the video with a better quality to every participant. When a user leaves the conference room \ac{KMS} has no need to decrease the participant's video quality as less network bandwidth will be used.

  \begin{figure}[!htb]
  \begin{center}
    \input{stats/test_client_net.tex}
  \end{center}
  \caption{Client Network usage during our test case}
  \label{fig:test_client_net}
\end{figure}

\subsubsection{Memory usage}

@@

\emph{KMS} memory usage was increasing and in fact we did not expected that, we have done more tests and we have observed that by disabling the recorder feature memory usage kept linearly related to the amount of clients present on the room. Therefore, we have verified our implementation and we have concluded that nothing was wrong with our code, we have confirmed that every allocated resource was indeed released after the end of recording. As a result of our intensive tests and consecutive failures we suspected that the problem was not ours.

Hence, in order to confirm our suspicions, we have decided to read the implementation of \ac{KMS} and we have found that \ac{KMS} was not releasing the memory if the recorder was stopped by us. Subsequently, we have changed the source code and submitted to \emph{Kurento} team through a \emph{GIT}'s \emph{"pull request"}.

Figure \ref{fig:test_ram_fixed_mem} shows the memory usage during our performance test case taking into account the patch that we applied to \ac{KMS}.

\begin{figure}[!htb]
  \begin{center}
    \input{stats/test_ram_fixed_mem.tex}
  \end{center}
  \caption{Memory usage after fixing recorder memory leak}
  \label{fig:test_ram_fixed_mem}
\end{figure}

\subsubsection{CPU usage}

@@

\subsubsection{Two consecutive test cases}

We have also performed two consecutive test cases in order to understand if we the influence of the first test case over the second, as observed in figure \ref{fig:test_two_times_cpu}, there is no \ac{CPU} influence between two test cases.

  \begin{figure}[!htb]
  \begin{center}
    \input{stats/test_two_times_cpu.tex}
  \end{center}
  \caption{Percentage of CPU used during two consecutive test cases}
  \label{fig:test_two_times_cpu}
\end{figure}

On the other hand due to memory recycling techniques we can observe in figure \ref{fig:test_two_times_mem} that some of the memory that was allocated in the first test was reused in the second case.

\begin{figure}[!htb]
  \begin{center}
    \input{stats/test_two_times_mem.tex}
  \end{center}
  \caption{Memory usage during two consecutive test cases}
  \label{fig:test_two_times_mem}
\end{figure}

\subsubsection{One hour test case}

   Figure \ref{fig:test_hour_mem} shows the memory used by our solution with seven clients simultaneously on the same conference room during one hour. As we can observe \ac{KMS} memory usage stabilizes.

  \begin{figure}[!htb]
  \begin{center}
    \input{stats/test_hour_mem.tex}
  \end{center}
  \caption{Memory usage during one hour with seven clients}
  \label{fig:test_hour_mem}
\end{figure}

### 2016-04-07 tese2/stats/test_ram_fixed_mem.tex
[ADD] client side tests

		\addplot[smooth,color=Blue] table[x expr=\thisrowno{0}-122,y expr=\thisrowno{1}/1000000] {stats/test_full_features/res_7_mongod.dat};
		\addlegendentry{Mongod}

		\addplot[smooth,color=Red] table[x expr=\thisrowno{0}-122,y expr=\thisrowno{1}/1000000] {stats/test_full_features/res_67_kurento-media-server.dat};
		\addlegendentry{Kurento Media Server}

		\addplot[smooth,color=Green] table[x expr=\thisrowno{0}-122,y expr=\thisrowno{1}/1000000] {stats/test_full_features/res_35_kurento-repo.dat};
		\addlegendentry{Kurento Repository}

		\addplot[smooth,color=Magenta] table[x expr=\thisrowno{0}-122,y expr=\thisrowno{1}/1000000] {stats/test_full_features/res_233_bash.dat};
		\addlegendentry{Java}

>>>>

		\addplot[smooth,color=Blue] table[x expr=\thisrowno{0}-68,y expr=\thisrowno{1}/1000000] {stats/test_ram_fixed/res_7_mongod.dat};
		\addlegendentry{Mongod}

		\addplot[smooth,color=Red] table[x expr=\thisrowno{0}-68,y expr=\thisrowno{1}/1000000] {stats/test_ram_fixed/res_67_kurento-media-server.dat};
		\addlegendentry{Kurento Media Server}

		\addplot[smooth,color=Green] table[x expr=\thisrowno{0}-68,y expr=\thisrowno{1}/1000000] {stats/test_ram_fixed/res_35_kurento-repo.dat};
		\addlegendentry{Kurento Repository}

		\addplot[smooth,color=Magenta] table[x expr=\thisrowno{0}-68,y expr=\thisrowno{1}/1000000] {stats/test_ram_fixed/res_233_bash.dat};
		\addlegendentry{Java}

### 2016-04-07 tese2/stats/test_two_times_cpu.tex
[ADD] client side tests

		\addplot[smooth,color=Blue] table[x expr=\thisrowno{0}-96,y index=1] {stats/test_two_times/cpu_7_mongod.dat};
		\addlegendentry{Mongod}

		\addplot[smooth,color=Red] table[x expr=\thisrowno{0}-96,y index=1] {stats/test_two_times/cpu_67_kurento-media-server.dat};
		\addlegendentry{Kurento Media Server}

		\addplot[smooth,color=Green] table[x expr=\thisrowno{0}-96,y index=1] {stats/test_two_times/cpu_35_kurento-repo.dat};
		\addlegendentry{Kurento Repository}

		\addplot[smooth,color=Magenta] table[x expr=\thisrowno{0}-96,y index=1] {stats/test_two_times/cpu_233_bash.dat};
		\addlegendentry{Java}

>>>>

		\addplot[smooth,color=Blue] table[x expr=\thisrowno{0}-72,y index=1] {stats/test_two_times3/cpu_7_mongod.dat};
		\addlegendentry{Mongod}

		\addplot[smooth,color=Red] table[x expr=\thisrowno{0}-72,y index=1] {stats/test_two_times3/cpu_68_kurento-media-server.dat};
		\addlegendentry{Kurento Media Server}

		\addplot[smooth,color=Green] table[x expr=\thisrowno{0}-72,y index=1] {stats/test_two_times3/cpu_35_kurento-repo.dat};
		\addlegendentry{Kurento Repository}

		\addplot[smooth,color=Magenta] table[x expr=\thisrowno{0}-72,y index=1] {stats/test_two_times3/cpu_234_bash.dat};
		\addlegendentry{Java}

### 2016-04-07 tese2/stats/test_two_times_mem.tex
[ADD] client side tests

		\addplot[smooth,color=Blue] table[x expr=\thisrowno{0}-96,y expr=\thisrowno{1}/1000000] {stats/test_two_times/res_7_mongod.dat};
		\addlegendentry{Mongod}

		\addplot[smooth,color=Red] table[x expr=\thisrowno{0}-96,y expr=\thisrowno{1}/1000000] {stats/test_two_times/res_67_kurento-media-server.dat};
		\addlegendentry{Kurento Media Server}

		\addplot[smooth,color=Green] table[x expr=\thisrowno{0}-96,y expr=\thisrowno{1}/1000000] {stats/test_two_times/res_35_kurento-repo.dat};
		\addlegendentry{Kurento Repository}

		\addplot[smooth,color=Magenta] table[x expr=\thisrowno{0}-96,y expr=\thisrowno{1}/1000000] {stats/test_two_times/res_233_bash.dat};
		\addlegendentry{Java}

>>>>

		\addplot[smooth,color=Blue] table[x expr=\thisrowno{0}-72,y expr=\thisrowno{1}/1000000] {stats/test_two_times3/res_7_mongod.dat};
		\addlegendentry{Mongod}

		\addplot[smooth,color=Red] table[x expr=\thisrowno{0}-72,y expr=\thisrowno{1}/1000000] {stats/test_two_times3/res_68_kurento-media-server.dat};
		\addlegendentry{Kurento Media Server}

		\addplot[smooth,color=Green] table[x expr=\thisrowno{0}-72,y expr=\thisrowno{1}/1000000] {stats/test_two_times3/res_35_kurento-repo.dat};
		\addlegendentry{Kurento Repository}

		\addplot[smooth,color=Magenta] table[x expr=\thisrowno{0}-72,y expr=\thisrowno{1}/1000000] {stats/test_two_times3/res_234_bash.dat};
		\addlegendentry{Java}
